Market Simulator

### 2020-08-18 analysis/05_market_simulator.Rmd
fixing person inputs and multi level inputs

@@

@@

@@

@@

@@

>>>>

    beta_persona$p1_value[beta_persona$levels == 'Persona 1'] <- 1

    beta_persona$p1_value[beta_persona$levels %in% input$p1_national_news == '0'] <- 0
    beta_persona$p1_value[beta_persona$levels == '1'] <- 1
    beta_persona$p1_value[beta_persona$levels == '2'] <- 2
    beta_persona$p1_value[beta_persona$levels == '3'] <- 3
    beta_persona$p1_value[beta_persona$levels == '4'] <- 4
    beta_persona$p1_value[beta_persona$levels == '5'] <- 5
    beta_persona$p1_value[beta_persona$levels == '6'] <- 6
    beta_persona$p1_value[beta_persona$levels == '7'] <- 7

@@

    beta_persona$p2_value[beta_persona$levels == 'Persona 2'] <- 1

    beta_persona$p2_value[beta_persona$levels == '0'] <- 0
    beta_persona$p2_value[beta_persona$levels == '1'] <- 1
    beta_persona$p2_value[beta_persona$levels == '2'] <- 2
    beta_persona$p2_value[beta_persona$levels == '3'] <- 3
    beta_persona$p2_value[beta_persona$levels == '4'] <- 4
    beta_persona$p2_value[beta_persona$levels == '5'] <- 5
    beta_persona$p2_value[beta_persona$levels == '6'] <- 6
    beta_persona$p2_value[beta_persona$levels == '7'] <- 7

@@

beta_test <- as.data.frame(matrix(rep(0), nrow = 13))

beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

beta_test$ai_issue <- 0
beta_test$ai_issue[4] <- 1
beta_test$ai_issue[8] <- 1
beta_test$ai_issue[9] <- 1

beta_test$gp_issue <- 0
beta_test$gp_issue[4] <- 1
beta_test$gp_issue[5] <- 1
beta_test$gp_issue[8] <- 1
beta_test$gp_issue[9] <- 1

beta_test$ox_issue <- 0
beta_test$ox_issue[4] <- 1
beta_test$ox_issue[6] <- 1
beta_test$ox_issue[8] <- 1
beta_test$ox_issue[9] <- 1

beta_test$rc_issue <- 0
beta_test$rc_issue[4] <- 1
beta_test$rc_issue[7] <- 1
beta_test$rc_issue[8] <- 1
beta_test$rc_issue[9] <- 1

  ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)

@@

exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)

@@

exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)

@@

selectInput("p1_national_news",
         label = "Follow national news:",
         choices = c('Multiple times a day' = "1",
                     'Every day' = "2",
                     "Once a week" = "3",
                     "Hardly ever" = "4",
                     "Never" = "5"),
         width = "200px")
